### 2013-09-19 nyu/paper.tex
new title, polish conclusion
typographic fine-tuning :)
spelling!

\section{Learning Depth-Sensitve Conditional Random Fields}\seclabel{learning}
We take a CRF approach, whose nodes represent a labeling of
superpixels.  We use an energy consisting of first and second order factors
(also called unary and pairwise potentials), with learned potential functions.
Let us denote the representation of an input image by $x$ and a labeling of
superpixels into semantic classes by $y$.  Then the general form of the energy is
\begin{equation}\eqlabel{energy}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
edges, encoding adjacence between superpixels.

@@

We found that our approach improves results most for scenes with a clear geometric structure,
which is not surprising. We see that evidence from the random forest is often very noisy, and biased
away from the ``props'' class. While the unstructured SVM can correct somewhat
for the class imbalance, it has no way to make larger areas consistent, which
the CRF can.
On the other hand, performance of the CRF deteriorates slightly on very crowded
scenes with a mixture of small furniture and prop objects, as
can be seen in the two right-most images. In these scenes, depth information is
often noisy, and it is hard to make geometric statements on the superpixel
level. As the input from the random forest is also often of low quality for
crowded scenes, the CRF has little chance to recover.

\begin{figure}
    \begin{center}
        \includegraphics[width=.45\linewidth]{nyu/images/vertical_alignment}
    \includegraphics[width=.45\linewidth]{nyu/images/depth_difference}
    \end{center}
    \caption{%
        Visualization of some of the learned potentials. The right potential is
        applied to relative depth between superpixels, the second on the
        feature encoding whether one superpixel is above the other in the
        image. See \secref{experiments} for details.
    \figlabel{weights}}
\end{figure}

\Figref{weights} visualizes some learned potential functions.
Higher values correspond to favored configurations. One can see that the
vertical alignment potential expresses that the floor is much more likely to be below
other classes. It also encodes the fact that props
rest on furniture, but not the other way around.
The potential of the depth feature encodes, for example, that the ground
is usually behind the other classes, while furniture is in front of structures,
such as the wall.
Interestingly, the potential functions are not anti-symmetric, and forcing them to be so
degrades the results. This suggests that the direction of connecting edges, going from
the top left to the bottom right in the image, is also exploited by the potentials.

@@

    \includegraphics[width=\linewidth]{nyu/images/00845_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00781_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01331_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00118_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01203_gt.png}\\
    \multicolumn{5}{@{}c@{}}{Ground Truth}\vspace{3mm}\\
    \multicolumn{5}{@{}c@{}}{%
        \includegraphics[]{nyu/legend.pdf}
    }
    \end{tabu}
\caption{%
Qualitative evaluation of the CRF\@.
The first three images illustrate errors in the original prediction that can be corrected, while
the second two images illustrate failure modes. Pixels marked as void
are excluded from the evaluation. See the \secref{results} for details.
\figlabel{comparison}}
\end{figure*}

>>>>

\section{Learning Depth-Sensitive Conditional Random Fields}\seclabel{learning}
We take a CRF approach, whose nodes represent a labeling of
superpixels.  We use an energy consisting of first and second order factors
(also called unary and pairwise potentials), with learned potential functions.
Let us denote the representation of an input image by $x$ and a labeling of
superpixels into semantic classes by $y$.  Then the general form of the energy is
\begin{equation}\eqlabel{energy}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates the superpixels, and $E\subset V \times V$ is a set of
edges, encoding adjacence between superpixels.

@@

We found that our approach improves results most for scenes with a clear geometric structure,
which is not surprising. We see that evidence from the random forest is often very noisy, and biased
away from the ``props'' class. While the unstructured SVM can correct somewhat
for the class imbalance, it has no way to make larger areas consistent, which
the CRF can.
On the other hand, performance of the CRF deteriorates slightly on very crowded
scenes with a mixture of small furniture and prop objects, as
can be seen in the two right-most images. In these scenes, depth information is
often noisy, and it is hard to make geometric statements on the superpixel
level. As the input from the random forest is also often of low quality for
crowded scenes, the CRF has little chance to recover.
%
\begin{figure}
    \begin{center}
        \includegraphics[width=.45\linewidth]{nyu/images/vertical_alignment}
    \includegraphics[width=.45\linewidth]{nyu/images/depth_difference}
    \end{center}
    \caption{%
        Visualization of some of the learned potentials. The right potential is
        applied to relative depth between superpixels, the second on the
        feature encoding whether one superpixel is above the other in the
        image. See \secref{experiments} for details.
    \figlabel{weights}}
\end{figure}
\pagebreak\\
%
\Figref{weights} visualizes some learned potential functions.
Higher values correspond to favored configurations. One can see that the
vertical alignment potential expresses that the floor is much more likely to be below
other classes. It also encodes the fact that props
rest on furniture, but not the other way around.
The potential of the depth feature encodes, for example, that the ground
is usually behind the other classes, while furniture is in front of structures,
such as the wall.
Interestingly, the potential functions are not anti-symmetric, and forcing them to be so
degrades the results. This suggests that the direction of connecting edges, going from
the top left to the bottom right in the image, is also exploited by the potentials.

@@

    \includegraphics[width=\linewidth]{nyu/images/00845_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00781_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01331_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00118_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01203_gt.png}\\
    \multicolumn{5}{@{}c@{}}{Ground Truth}\vspace{3mm}\\
    \multicolumn{5}{@{}c@{}}{%
        \includegraphics[]{nyu/legend.pdf}
    }
    \end{tabu}
\caption{%
Qualitative evaluation of the CRF\@.
The first three images illustrate errors in the original prediction that can be corrected, while
the second two images illustrate failure modes. Pixels marked as void
are excluded from the evaluation. See \Secref{experiments} for details.
\figlabel{comparison}}
\end{figure*}

### 2013-09-19 partial_supervision/paper.tex
spelling!

In our model, each image forms a bag, while the candidate segments correspond
to the instances contained in the bag. During learning, only presence of object
classes is needed as bag level supervision. By learning $f_{I}$, we are then
able to predict for individual segments whether they contain the object class
of interest, thereby obtaining a segmentation of the object.
To measure the performance of our algorithm, we use a dataset that not only contains
image level annotation, but also pixel level annotation of object. This allows
us to judge the succes of learning on instance level.

@@

\subsection{Semantic Scene Segmentation using Weak Annotation}
Learning semantic segmentation from image-level annotation was first investigated in \citet{verbeek2007region},
using a semi-supervised conditional random field on patches. \citet{verbeek2007region} evaluated their approach
on the MSRC-9 datasets.
More recently, simliar approaches were proposed by
\citet{vezhnevets2011weakly} and \citet{vezhnevets2010towards}.
\citet{vezhnevets2011weakly} independently developed a multiple-instance based
approach to segmentation, and report impressinve results on the MSRC-21 dataset.

While semantic segmentation is closely related to the task of multi-class image
segmentation that we are considering in this chapter, there are important
distinctions: In semantic segmentation, each pixel has a semantic annotation,
also containing non-object ``stuff'' classes like ``sky'', ``grass'' and
``water''. In multi-class image segmentation, the focus is on objects, with
possibly large parts of the image being labeled as unspecific ``background''.
The unspecific background class contains much more clutter than for example
``grass'' and is therefore much harder to model. Additionally, object classes
themselves are much harder to capture using low-level textural information
only.  This makes disseminating the distinctive features in multi-class object
recognition much more challenging, and requires a more holistic apporach to
recognition than these patch-based or superpixel-based approaches.

@@

\end{table}
We compared the performance of MIK, MIK-I and state-of-the-art MI
methods on the Musk benchmark datasets~\citep{dietterich1997solving} in
\Tabref{muskacc}. Results were obtained using 10-fold cross-validation. While
the computational complexity of MIK-I is very low compared to the other
methods, it achieves competitive results.  Using instance-level labels results
in a slight loss of accuracy of MIK-I, compared to MIK\@. Interestingly, even
though the model was not trained to provide any instance-level labels, the
performance is still competative.

>>>>

In our model, each image forms a bag, while the candidate segments correspond
to the instances contained in the bag. During learning, only presence of object
classes is needed as bag level supervision. By learning $f_{I}$, we are then
able to predict for individual segments whether they contain the object class
of interest, thereby obtaining a segmentation of the object.
To measure the performance of our algorithm, we use a dataset that not only contains
image level annotation, but also pixel level annotation of object. This allows
us to judge the success of learning on instance level.

@@

\subsection{Semantic Scene Segmentation using Weak Annotation}
Learning semantic segmentation from image-level annotation was first investigated in \citet{verbeek2007region},
using a semi-supervised conditional random field on patches. \citet{verbeek2007region} evaluated their approach
on the MSRC-9 datasets.
More recently, similar approaches were proposed by
\citet{vezhnevets2011weakly} and \citet{vezhnevets2010towards}.
\citet{vezhnevets2011weakly} independently developed a multiple-instance based
approach to segmentation, and report impressive results on the MSRC-21 dataset.

While semantic segmentation is closely related to the task of multi-class image
segmentation that we are considering in this chapter, there are important
distinctions: In semantic segmentation, each pixel has a semantic annotation,
also containing non-object ``stuff'' classes like ``sky'', ``grass'' and
``water''. In multi-class image segmentation, the focus is on objects, with
possibly large parts of the image being labeled as unspecific ``background''.
The unspecific background class contains much more clutter than for example
``grass'' and is therefore much harder to model. Additionally, object classes
themselves are much harder to capture using low-level textural information
only.  This makes disseminating the distinctive features in multi-class object
recognition much more challenging, and requires a more holistic approach to
recognition than these patch-based or superpixel-based approaches.

@@

\end{table}
We compared the performance of MIK, MIK-I and state-of-the-art MI
methods on the Musk benchmark datasets~\citep{dietterich1997solving} in
\Tabref{muskacc}. Results were obtained using 10-fold cross-validation. While
the computational complexity of MIK-I is very low compared to the other
methods, it achieves competitive results.  Using instance-level labels results
in a slight loss of accuracy of MIK-I, compared to MIK\@. Interestingly, even
though the model was not trained to provide any instance-level labels, the
performance is still competitive.

### 2013-09-19 pystruct/paper.tex
spelling!

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_models}Comparison of models implemented
    in popular structured prediction software packages. LSVM stands for the latent multi-class SVM, LDCRF for
    latend dynamic conditional random fields.}
\end{table}

@@

\section{Summary}
Im this chapter, we introduced basic concepts of structured prediction. In particular, we discussed
Structured Support Vector Machines, a max-margin approach for training linear predictors for
structured data. %TODO comparison of algorithms?
We gave a description of several popular learning algorithms, together with their theoretical
runtime bounds and practical considerations.
%TODO summarize structured prediction
We also introduced \pystruct, our modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations and is be the
basis of our further experiments.
\pystruct integrates itself into the scientific Python ecosystem, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches.
In the future, we plan to integrate other paradigms, such as sampling-based
learning~\citep{wick2011samplerank}, surrogate objectives (for example
pseudo-likelihood), and approaches that allow for a better integration of
inference and learning~\citep{meshi2010learning}.

>>>>

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_models}Comparison of models implemented
    in popular structured prediction software packages. LSVM stands for the latent multi-class SVM, LDCRF for
    latent dynamic conditional random fields.}
\end{table}

@@

\section{Summary}
In this chapter, we introduced basic concepts of structured prediction. In particular, we discussed
Structured Support Vector Machines, a max-margin approach for training linear predictors for
structured data. %TODO comparison of algorithms?
We gave a description of several popular learning algorithms, together with their theoretical
runtime bounds and practical considerations.
%TODO summarize structured prediction
We also introduced \pystruct, our modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations and is be the
basis of our further experiments.
\pystruct integrates itself into the scientific Python ecosystem, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches.
In the future, we plan to integrate other paradigms, such as sampling-based
learning~\citep{wick2011samplerank}, surrogate objectives (for example
pseudo-likelihood), and approaches that allow for a better integration of
inference and learning~\citep{meshi2010learning}.

### 2013-09-19 structured_prediction/paper.tex
typos julia
spelling!

This approach to structured prediction is closely related to 
approaches using \emph{probabilistic graphical models}.  Probabilistic graphical models are a
tool to express factorizations of probability distributions.  Similar to
\Eqref{log_factor_graph}, the joint probability distribution over a
multi-variate random variable $y$ can be expressed using a factor-graph:
\begin{equation}\eqlabel{graphicalmodel}
    p(y | x) = \frac{1}{Z_x}\prod_{F \in \mathcal{F}} \exp\left(\psi_F(x, y_{N_F})\right).
\end{equation}
Here
\begin{equation}
    Z_x = \sum_{y' \in \mathcal{Y}} \prod_{F \in \mathcal{F}} \exp\left(\psi(x, y'_{N_F})\right)
\end{equation}
is the normalization constant of the conditional distribution over $y$.
If $f$ is chosen as in \Eqref{linear_psi}, then the resulting distribution
belongs to the exponential family, the class of probablility distributions most
commonly used in the graphical model iterature.

@@

\subsection{The 1-Slack Cutting Plane Method}\seclabel{one_slack}

\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State 
            \vspace{-5mm}
            \begin{align*}
            (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:\\
            &\theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi
            \end{align*}
            \For {i=1, \dots, k}
                \State
                $\hat{y}\hoch{i} \leftarrow I(x\hoch{i}, y\hoch{i}, \theta) := \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
            \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

The $1$-slack cutting plane method~\citep{joachims2009cutting} solves the
following reformulation of Equation~\Eqref{learning_equation}:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
\enlargethispage{10mm}
Informally, the $1$-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points, and
then applying the $n$-slack algorithm with a single data point.\pagebreak\\
A detailed description can be found in Algorithm~\ref{alg_one_slack}.
%
By construction, only a single constraint is added in each iteration of
Algorithm~\ref{alg_one_slack}, leading to very small working sets $\W$.
This has the advantage of producing a QP that easyer to solve, as it contains far
less variables than in the $n$-slack algorithm. The down-side of this is that
the loss-augmented prediction problem has to be solved much more often until
convergence. This is reflected in a convergence rate of $O(\frac{1}{kT})$,
which scales with the inverse of the dataset size.

>>>>

This approach to structured prediction is closely related to 
approaches using \emph{probabilistic graphical models}.  Probabilistic graphical models are a
tool to express factorizations of probability distributions.  Similar to
\Eqref{log_factor_graph}, the joint probability distribution over a
multi-variate random variable $y$ can be expressed using a factor-graph:
\begin{equation}\eqlabel{graphicalmodel}
    p(y | x) = \frac{1}{Z_x}\prod_{F \in \mathcal{F}} \exp\left(\psi_F(x, y_{N_F})\right).
\end{equation}
Here
\begin{equation}
    Z_x = \sum_{y' \in \mathcal{Y}} \prod_{F \in \mathcal{F}} \exp\left(\psi(x, y'_{N_F})\right)
\end{equation}
is the normalization constant of the conditional distribution over $y$.
If $f$ is chosen as in \Eqref{linear_psi}, then the resulting distribution
belongs to the exponential family, the class of probability distributions most
commonly used in the graphical model literature.

@@

\subsection{The $1$-Slack Cutting Plane Method}\seclabel{one_slack}

\begin{algorithm*}[t]
    \caption{$1$-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State 
            \vspace{-5mm}
            \begin{align*}
            (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:\\
            &\theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi
            \end{align*}
            \For {i=1, \dots, k}
                \State
                $\hat{y}\hoch{i} \leftarrow I(x\hoch{i}, y\hoch{i}, \theta) := \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
            \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

The $1$-slack cutting plane method~\citep{joachims2009cutting} solves the
following reformulation of Equation~\Eqref{learning_equation}:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
\enlargethispage{10mm}
Informally, the $1$-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points, and
then applying the $n$-slack algorithm with a single data point.\pagebreak\\
A detailed description can be found in Algorithm~\ref{alg_one_slack}.
%
By construction, only a single constraint is added in each iteration of
Algorithm~\ref{alg_one_slack}, leading to very small working sets $\W$.
This has the advantage of producing a QP that easier to solve, as it contains far
less variables than in the $n$-slack algorithm. The down-side of this is that
the loss-augmented prediction problem has to be solved much more often until
convergence. This is reflected in a convergence rate of $O(\frac{1}{kT})$,
which scales with the inverse of the dataset size.
